---
title: "Animal Population in India"
author: Deepti Chauhan
date: July 31, 2020
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This is a Shiny App which shows the population of elephants, tigers and leopards in different states of India.
The side panel gives the option of selecting one or more of the animals
On the main panel is a map drawn using Leaflet package to dynamically show the population. The size of the circle corresponds to the population.
The color of circle corresponds to the animal selected.
On clicking on the icons, the user can see the details - Name of the state, name of the animal and the population

## Input

The app takes in input in terms of whether they want to see the population of elephants, tigers and leopards in Indian states. The user is provided a checkbox input type option in the side panel. 

## Output
```{r echo = TRUE}
library(shiny)
library(leaflet)
shinyUI(fluidPage(

    # Application title
    titlePanel("Animal Population in India"),

    # Sidebar with a slider input for number of bins
    sidebarLayout(
        sidebarPanel(
			h3("Choose Animals"),
			checkboxInput("elephant", "Elephants", value = TRUE),
			checkboxInput("tiger", "Tigers", value = FALSE),
			checkboxInput("leopard", "Leopards", value = FALSE),
        ),

        # Show a plot of the generated distribution
        mainPanel(
            h3("Population of Animals in Indian States"),
	    leafletOutput("mapPlot"),
        )
    )
))
```
```{r echo = FALSE}

# Define server logic required to draw a histogram
shinyServer(function(input, output) {

    output$mapPlot <- renderLeaflet({

		checkElephants <- input$elephant
		checkTigers <- input$tiger
		checkLeopards <- input$leopard

		animalIcon <- iconList(
		  elephantIcon = makeIcon("https://static.thenounproject.com/png/9587-200.png", "https://static.thenounproject.com/png/9587-200.png", 24, 24),
		  tigerIcon = makeIcon("https://static.thenounproject.com/png/912730-200.png", "https://static.thenounproject.com/png/912730-200.png", 24, 24),
		  leopardIcon = makeIcon("https://static.thenounproject.com/png/246357-200.png", "https://static.thenounproject.com/png/246357-200.png", 24, 24)
		)

		md_states <- data.frame(name = c("Andhra Pradesh", "Arunachal Pradesh", "Assam", "Bihar",
										 "Chhattisgarh", "Goa", "Gujarat", "Jharkhand", "Karnataka", "Kerala","Madhya Pradesh","Maharashtra","Meghalaya","Mizoram","Nagaland","Odisha","Rajasthan","Tamil Nadu","Tripura","Uttar Pradesh","Uttarakhand","West Bengal"),
								pop_elephants = c(65, 1614, 5719, 25, 247, 0, 0, 679, 6049, 3054,7,6,1754,7,432,1966,84,2761,102,232,1839,194),
								pop_tigers = c( 0, 679, 6049, 5719, 25, 247, 0,1966,84,2761,102,232,3054,7,6,1754,7,432,65, 1614,1839,194),
								pop_leopards = c( 247, 0, 0, 25, 3054,7,1614, 5719,232,1839,194,6,1754,7,432,1966,84,2761,102,679, 6049,65),
								lat = c(14.7504291,27.10039878, 26.7499809, 25.78541445, 22.09042035, 15.491997, 23, 	23.80039349, 12.57038129, 	8.900372741, 21.30039105, 19.25023195, 25.57049217, 23.71039899, 25.6669979, 19.82042971, 	26.44999921, 	12.92038576, 23.83540428, 27.59998069, 30.32040895, 	22.58039044),
								lng = c(78.57002559,93.61660071, 94.21666744, 87.4799727, 82.15998734, 73.81800065, 72, 86.41998572, 	76.91999711, 76.56999263, 76.13001949, 	73.16017493, 	91.8800142, 92.72001461, 	94.11657019, 85.90001746, 74.63998124, 79.15004187, 91.27999914, 78.05000565, 78.05000565, 88.32994665))
		if(checkElephants==TRUE && checkTigers==TRUE && checkLeopards==TRUE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$elephantIcon, popup = paste(md_states$name," elephants ",md_states$pop_elephants)) %>%
				addCircles(weight = 1, radius = md_states$pop_elephants*100, color = c("navy blue","red","orange")) %>%
				addMarkers(icon = animalIcon$tigerIcon, popup = paste(md_states$name," tigers ",md_states$pop_tigers)) %>%
				addCircles(weight = 1, radius = md_states$pop_tigers*100, color = "red") %>%
				addMarkers(icon = animalIcon$leopardIcon, popup = paste(md_states$name," leopards ",md_states$pop_leopards)) %>%
				addCircles(weight = 1, radius = md_states$pop_leopards*100, color = "orange")
		}
		else if(checkElephants==TRUE && checkTigers==TRUE && checkLeopards==FALSE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$elephantIcon, popup = paste(md_states$name," elephants ",md_states$pop_elephants)) %>%
				addCircles(weight = 1, radius = md_states$pop_elephants*100, color = "navy blue") %>%
				addMarkers(icon = animalIcon$tigerIcon, popup = paste(md_states$name," tigers ",md_states$pop_tigers)) %>%
				addCircles(weight = 1, radius = md_states$pop_tigers*100, color = "red")
		}
		else if(checkElephants==TRUE && checkTigers==FALSE && checkLeopards==TRUE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$elephantIcon, popup = paste(md_states$name," elephants ",md_states$pop_elephants)) %>%
				addCircles(weight = 1, radius = md_states$pop_elephants*100, color = "navy blue") %>%
				addMarkers(icon = animalIcon$leopardIcon, popup = paste(md_states$name," leopards ",md_states$pop_leopards)) %>%
				addCircles(weight = 1, radius = md_states$pop_leopards*100, color = "orange")
		}
		else if(checkElephants==FALSE && checkTigers==TRUE && checkLeopards==TRUE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$tigerIcon, popup = paste(md_states$name," tigers ",md_states$pop_tigers)) %>%
				addCircles(weight = 1, radius = md_states$pop_tigers*100, color = "red") %>%
				addMarkers(icon = animalIcon$leopardIcon, popup = paste(md_states$name," leopards ",md_states$pop_leopards)) %>%
				addCircles(weight = 1, radius = md_states$pop_leopards*100, color = "orange")
		}
		else if(checkElephants==TRUE && checkTigers==FALSE && checkLeopards==FALSE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$elephantIcon, popup = paste(md_states$name," elephants ",md_states$pop_elephants)) %>%
				addCircles(weight = 1, radius = md_states$pop_elephants*100, color = "navy blue")
		}
		else if(checkElephants==FALSE && checkTigers==TRUE && checkLeopards==FALSE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$tigerIcon, popup = paste(md_states$name," tigers ",md_states$pop_tigers)) %>%
				addCircles(weight = 1, radius = md_states$pop_tigers*100, color = "red")
		}
		else if(checkElephants==FALSE && checkTigers==FALSE && checkLeopards==TRUE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles() %>%
				addMarkers(icon = animalIcon$leopardIcon, popup = paste(md_states$name," leopards ",md_states$pop_leopards)) %>%
				addCircles(weight = 1, radius = md_states$pop_leopards*100, color = "orange")
		}
		else if(checkElephants==FALSE && checkTigers==FALSE && checkLeopards==FALSE)
		{
			md_states %>%
			  leaflet() %>%
			  addTiles()
		}

    })

})
```

## Final Slide

Thank You!
